---
title: "5 Line Segments Results"
output: html_notebook
---
# Setup
```{r Libraries, echo=FALSE,message=FALSE}
library(afex)
library(lme4)
library(effectsize)
library(magrittr)
library(ggpubr)
library(ggplot2)

threshReduction <- function(value,baseline){
  return ((value-baseline) / baseline)
}
```
Finish data frames
```{r, DFs}
rmPeople <- FALSE
getLeverage <- FALSE
rmWho <- c() # cooks distance

dfGLM <- read.csv('dfGLM.csv', stringsAsFactors = TRUE)
if(rmPeople){dfGLM %<>% subset(!Participant_Number %in% rmWho)} # Remove problematic points
dfGLM$id %<>% as.factor() %>% droplevels()
dfGLM$label %<>% as.factor()


df2Way <- read.csv('df2Way.csv', stringsAsFactors = TRUE)
if(rmPeople){df2Way %<>% subset(!Participant_Number %in% rmWho)} # Remove problematic points
df2Way$id %<>% as.factor() %>% droplevels()
df2Way$label %<>% as.factor()

df1Way <- read.csv("df1Way_fromPy.csv", stringsAsFactors = TRUE)
if(rmPeople){df_python %<>% subset(!id %in% rmWho)} # Remove problematic points
df1Way$id %<>% as.factor() %>% droplevels()
df1Way$label %<>% as.factor()
df1Way$threshold_michelson_c <- scale(df1Way$threshold_michelson, scale = F) %>% c()
```

# Stats
## GLM + LRT
Should models here use `baseline` as a continuous predictor? It may explain additional variance, but it is not necessarily interesting. The lower your baseline threshold is, the better you are at seeing the target. Thus you would expect to see a large negative estimate.

Baseline can either be modeled by adding into the formula a `+ baseline`.

### Using Nominal Factors
This mode uses the factorized versions of the flanker contrast variables: `label`.
```{r GLMfactor, warning=F}
conds <- dfGLM$label %>% levels()
contrasts <- list('label' = contr.treatment(n = conds, base = which(conds == '0')))
Control <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 3e8),
                         check.conv.grad = .makeCC("warning", tol = 0.005, relTol = NULL))

model_glm_f <- glmer(data = dfGLM, 
                    formula = "responseRate ~ TC_michelson_c * label + (1|id)",
                    family = binomial('logit'),
                    weights = weights,
                    contrasts = contrasts,
                    control = Control)
dfGLM$probability_f <- predict(model_GLM_f,type='response', re.form = NA)

model_lrt_f <- mixed(data = dfGLM,
                    formula = "responseRate ~ TC_michelson_c * label + (1|id)",
                    family = binomial('logit'),
                    weights = weights,
                    type = 3,
                    method = 'LRT',
                    control = Control)
model_lrt_f
```
### Using Continuous Predictors
This mode uses the numeric (and centered) versions of the flanker contrast variables: `FC_michelson_c`.
```{r GLMnumeric, warning=F}
model_GLM_n <- glmer(data = dfGLM,
                     formula = "responseRate ~ TC_michelson_c * FC_michelson_c + (1|id)",
                     family = binomial('logit'),
                     weights = weights,
                     control = Control)
dfGLM$probability_n <- predict(model_GLM_n,type='response', re.form = NA)

model_LRT_n <- mixed(data = dfGLM,
                     formula = "responseRate ~ TC_michelson_c * FC_michelson_c  + (1|id)",
                     family = binomial('logit'),
                     weights = weights,
                     type = 3,
                     method = 'LRT',
                     control = Control)
model_LRT_n
```

## 1-Way ANOVA
ANOVA using the percent of baseline contrast (`label`).
```{r 1way, warning=F}
model_2wayPy <- aov_ez(data = df1Way,
                       id = 'id',
                       dv = 'threshold_michelson_c',
                       within = c('label'),
                       type = 3,
                       anova_table = list(es = 'pes', MSE = FALSE,
                                        p_adjust_method = 'none', 
                                        correction = 'GG'))
model_2wayPy
emmeans::emmeans(model_2wayPy, specs = ~ label) %>% pairs()
```
## 2-Way ANOVA
Same as the 1-way, however, now we add `TC_f` as a predictor.
```{r 2way, warning=T}
model_2way <- aov_ez(data = df2Way,
                     id = "id",
                     dv = "responseRate",
                     within = c("label","TC_f"),
                     type = 3,
                     anova_table = list(es = 'pes', MSE = FALSE,
                                        p_adjust_method = 'none', 
                                        correction = 'GG'))
model_2way
emmeans::emmeans(model_2way, specs = ~ label | TC_f) %>% pairs()
```

# Plotting
```{r aes, include=F, echo=F}
colors <- RColorBrewer::brewer.pal(length(conds),'Dark2')
Palette <- setNames(colors,conds)

newDat <- expand.grid(label = conds,
                      TC_michelson_c = seq(min(dfGLM$TC_michelson_c),
                                           max(dfGLM$TC_michelson_c),
                                           .0001))

newDat$probability_f <- predict(model_glm_f, re.form = NA, type = 'response', newdata = newDat)
```
## GLM
```{r glmPlot, echo=F}
ggplot(data = newDat,
       mapping = aes(x = TC_michelson_c + weighted.mean(dfGLM$TC_michelson,dfGLM$weights), 
                     y = probability_f,
                     color = label)) +
  geom_line(linewidth = 1.3) +
  scale_x_continuous(transform = 'log10') +
  scale_color_manual(
    values = Palette,
    name = "Flanker\nContrast") +
  xlab('Target Contrast') +
  ylab('Detection Probability') +
  geom_hline(yintercept = .5, linetype = 'dashed') +
  ylim(0,1) +
  theme_pubr() +
  theme(text = element_text(size = 16, family = 'Times'),
        legend.position = 'right')
ggsave("/Users/harrysteinharter/Documents/MSc/Thesis_Overview/Experiment_6/images6/Exp6GLM.png")
```

## 1-Way ANOVA Plot
```{r 1wayPlot, echo=F}
dodgeWidth = .9
ggplot(data = df1Way,
       mapping = aes(x = label, y = threshold,
                     color = I('black'), fill = label)) +
  stat_summary(geom = 'bar',
               fun = 'mean',
               position = position_dodge(dodgeWidth),
               show.legend = FALSE) +
  stat_summary(geom = 'errorbar',
               fun.data = mean_cl_normal,
               position = position_dodge(dodgeWidth),
               width = .2,) +
  scale_fill_manual(
    values = Palette) +
  xlab("Flanker Contrast") +
  ylab('Detection Threshold') +
  theme_pubr() +
  theme(text = element_text(size = 16, family = 'Times'),
        legend.position = 'right')
ggsave("/Users/harrysteinharter/Documents/MSc/Thesis_Overview/Experiment_6/images6/Exp6ANOVA.png")
```
## Percent Facilitation Plot
```{r facilPlot, echo=F}
df1Way %<>%
  mutate(reduction = threshReduction(threshold_michelson, baseline_michelson))

ggplot(data = df1Way,
       mapping = aes(x = label, y = reduction)) +
  geom_hline(yintercept = 0,
             linetype = 'dashed') +
  stat_summary(geom = 'errorbar',
               width = .2,
               fun.data = mean_cl_normal) +
  stat_summary(geom = 'line',
               mapping = aes(group = 1),
               fun = mean) +
  stat_summary(geom = 'point',
               mapping = aes(color = label),
               size = 4,
               fun = mean,
               show.legend = FALSE) +
  scale_color_manual(values = Palette) +
  xlab("Flanker Contrast") +
  ylab("Threshold Reduction") +
  theme_pubr() +
  theme(text = element_text(size = 16, family = 'times'))
ggsave("/Users/harrysteinharter/Documents/MSc/Thesis_Overview/Experiment_6/images6/Exp6ThresholdReduction.png")
```


## 2-Way ANOVA Plot
```{r 2wayPlot, echo=F}
dodgeWidth = .9
ggplot(data = df2Way,
       mapping = aes(x = TC_f %>% factor(c('Low','Medium','High')), y = responseRate,
                     fill = label, color = I('black'))) +
  stat_summary(geom = 'bar',
               fun = 'mean',
               position = position_dodge(dodgeWidth),
               width = dodgeWidth) +
  stat_summary(geom = 'errorbar',
               fun.data = mean_cl_normal,
               position = position_dodge(dodgeWidth),
               width = .2) +
  scale_fill_manual(values = Palette,
                     name = "Flanker\nContrast") +
  ylim(0,1) +
  xlab('Flanker Contrast') +
  ylab('Mean Response Rate') +
  theme_pubr() +
  theme(text = element_text(size = 16, family = 'Times'),
        legend.position = 'right')
ggsave("/Users/harrysteinharter/Documents/MSc/Thesis_Overview/Experiment_6/images6/Exp6ANOVA2.png")
```

